Solutions to Integer Programming from Quantum Annealing

### 2020-08-30 paper/main.tex
fancy names
add offset section in appendix

%! suppress = LineBreak
\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,
floatfix,longbibliography]{revtex4-2}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{bm,bbm}
\usepackage{graphicx}
\usepackage{xcolor}

@@

\author{Chia~Cheng~Chang}
\affiliation{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
\author{Chih-Chieh~Chen}
\affiliation{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
\author{Christopher K\"orber}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
\author{Travis~Humble}
\affiliation{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
\author{Jim~Ostrowski}
\affiliation{University of Tennessee}

@@

The resulting probability of recovering the correct solution as a function of annealing offset is given in Fig.~\ref{fig:dwave1us}. We confirm that scaling with respect to offset from the simulation matches what is observed from experiment. Furthermore, in Sec.~\ref{}, we provide the results of an ideal quantum annealer, where the annealing schedule is faithfully delayed (all qubits start and end with the same values of $A$ and $B$) and all decoherence terms are removed. The scaling with respect to offset is preserved indicating that the improvements are related to quantum mechanics.

@@

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \mathcal{L}[\rho (t)] ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$. $H(t)$ is the time-dependent Hamiltonian 
\begin{align}
\label{eq:annealH}
 H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\ 
 +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
\end{align}
where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions. The site dependency takes into account of the annealing offset. $[,]$ denotes the Lie bracket and $\mathcal{L}$ is the Lindblad operator.

@@

>>>>

%! suppress = LineBreak
\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,
floatfix,longbibliography]{revtex4-2}
\usepackage{CJK}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{bm,bbm}
\usepackage{graphicx}
\usepackage{xcolor}

@@

\author{Chia~Cheng~Chang (\begin{CJK*}{UTF8}{bsmi}張家丞\end{CJK*})}
\affiliation{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
	\author{Chih-Chieh~Chen (\begin{CJK*}{UTF8}{bsmi}\mbox{陳志傑}\end{CJK*})}
\affiliation{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
\author{Christopher K\"orber}
\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
\author{Travis~Humble}
\affiliation{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
\author{Jim~Ostrowski}
\affiliation{University of Tennessee}

@@

The resulting probability of recovering the correct solution as a function of annealing offset is given in Fig.~\ref{fig:dwave1us}. We confirm that scaling with respect to offset from the simulation matches what is observed from experiment, and provides evidence suggesting that the improvements are related to quantum mechanics. An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets is presented in Sec.~\ref{sec:app:offset}, and further supports this observation.

@@

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \mathcal{L}[\rho (t)] ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$. The time-dependent Hamiltonian $H(t)$ solved by DWave as documented in Ref.~\cite{dwave_offset} is
\begin{align}
\label{eq:annealH}
 H^{\textrm{anneal}}(t)  =&  - \sum_i  A_i(t)\sigma^x_i +\sum_i B_{i}(t) h_i \sigma^z_i \notag \\
 +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j ,&
\end{align}
where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions. The site dependency takes into account of the annealing offset. $[,]$ denotes the Lie bracket and $\mathcal{L}$ is the Lindblad operator.

@@

\subsection{Systematic effects of annealing offsets}
\label{sec:app:offset}
We verify that our implementation of annealing offsets on the simulator is consistent with DWave by solving the following three qubit Hamiltonian
\begin{align}
	\label{eq:offset_test_hamiltonian}
	H^{\textrm{problem}} =
	\begin{pmatrix}
		-0.25 & 1 & 0 \\
		0 & -0.25 & 0 \\
		0 & 0 & -0.25
	\end{pmatrix}
\end{align}
which has a doubly-degenerate ground state of $(0, 1, 1)$ and $(1, 0, 1)$. An annealing offset is then applied to either qubit 0 or 1, and breaks the ground state degeneracy of the system. Because of the systematic error introduced when assigning an offset to a qubit, the final Hamiltonian given by Eq.~(\ref{eq:annealH}) will have small deviations from the input problem Hamiltonian. For example, we expect a negative offset to qubit 0 to Eq.~(\ref{eq:offset_test_hamiltonian}) will yield $(1, 0, 1)$ as the unique ground state given Eq.~(\ref{eq:annealH}).

We confirm that with different combinations of annealing offsets, the degeneracy is lifted on the DWave results as expected by solving for the modified problem Hamiltonian spectrum, as well as dialing in annealing offset in the simulation of this three qubit test case.

In the simulation, we are also reserve the ability to remove the systematic errors by extending the annealing schedule as shown in Fig.~\ref{fig:anneal_schedule_ext}. With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians. The dependence on offset for $G(2)$ (Fig.~(\ref{fig:dwave1us})) remains the same under the extended anneal schedule (Fig.~\ref{fig:anneal_schedule_ext}), confirming that the behavior is not a systematic artifact.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./new_figures/anneal_schedule_extended.pdf}
	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling_extended.pdf}
	\caption{{\color{red}I need to add dwave final state distribution here too.}}
	\label{fig:anneal_schedule_ext}
\end{figure}
